---
title: "3: W35: Start with R"
author: Anja Meerwald 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

2:W35: Start with R
DESCRIPTION

Instructions: For this assignment, you need to answer a couple questions with code and then take a screenshot of your working environment.

Submit the solutions including the URL to the screenshot in a doc/pdf to Brightspace.

1) Use R to figure out how many elements in the vector below are greater than 2 and then tell me what their sum (of the larger than 2 elements) is.

```{r}
rooms <- c(1, 2, 4, 5, 1, 3, 1, NA, 3, 1, 3, 2, 1, NA, 1, 8, 3, 1, 4, NA, 1, 3, 1, 2, 1, 7, 1, 9, 3, NA)
```


```{r}
# showing the amount of elements greater than 2 in the vector, including NAs
rooms[rooms>2]
```


```{r}
# calculating the total number of rooms greater than 2 (=12)
sum(rooms>2, na.rm = TRUE)
```


```{r}
# removing the NAs
rooms_omitNA <- na.omit(rooms)

# creating a new vector with only rooms 3 or more 
big_rooms <- rooms_omitNA[!(rooms_omitNA < 3)]

# the total of those amount of rooms, 55 
sum(big_rooms)
  
```

2) What type of data is in the 'rooms' vector?

```{r}
class(rooms)
```

3) Submit the following image to Github: Inside your R Project (.Rproj), install the 'tidyverse' package and use the download.file() and read_csv() function to read the SAFI_clean.csv dataset into your R project as 'interviews' digital object (see instructions in https://datacarpentry.org/r-socialsci/setup.html and 'Starting with Data' section). Take a screenshot of your RStudio interface showing

a) the line of code you used to create the object,

b) the 'interviews' object in the Environment, and

c) the file structure of your R project in the bottom right "Files" pane.

Save the screenshot as an image and put it in your AUID_lastname_firstname repository inside our Github organisation (github.com/Digital-Methods-HASS) or equivalent. Place here the URL leading to the screenshot in your repository.

file:///Users/anjameerwald/Desktop/Screen%20Shot%202022-09-04%20at%204.08.24%20PM.png

```{r}
library(tidyverse)

interviews <- read_csv("data/SAFI_clean.csv", na = "NULL")

# can also use the downlaod.file() command but didn't need to since I have the file already in my data folder 
# download.file("https://ndownloader.figshare.com/files/11492171","data/SAFI_clean.csv", mode = "wb")

```

4) Challenge: If you managed to create your own Danish king dataset, use it. If not, you the one attached to this assignment (it might need to be cleaned up a bit). Load the dataset into R as a tibble. Calculate the mean() and median() duration of rule over time and find the three mondarchs ruling the longest. How many days did they rule (accounting for transition year?)

```{r}
kings <- read_csv2("data/kings.csv")

# removing NAs and putting it into a new df 
kings_noNA <- na.omit(kings)

# getting a overview of what the df looks like 
str(kings_noNA)

# making the yearsaruler variable numeric 
kings_noNA$Yearasruler <- as.numeric(kings_noNA$Yearasruler)

str(kings_noNA)

# mean of the years a ruler variable 
mean(kings_noNA$Yearasruler) 

# median of the years a ruler variable 
median(kings_noNA$Yearasruler)

# can see the kings in order from most years to least years 
kings_noNA %>% 
  arrange(desc(Yearasruler))

# working with just the top three rulers in terms of time and putting them into their own data frame  
kings_top <- kings_noNA %>% 
  arrange(desc(Yearasruler)) %>% 
  slice(1:3)
kings_top
  
# multiplying the years a ruler column by 365 days in a year and adding another 365 for the transition year; also adding it to the kings top data frame  
kings_top$years2days <- (kings_top$Yearasruler*365) + 365
kings_top

```


