---
title: "So Cult"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Packages 
```{r, include = FALSE}

library(tidyverse, dplyr)
pacman::p_load(ggplot2,
               tidyr,
               ggpubr,
               rstatix)

```


Load in data 
```{r, include = FALSE}

df <- read_csv("data/Sex Survey.csv")

repo_df <- read_csv("data/Reproduction Sex Survey.csv")
```

```{r}
# renaming all the columns 
names(df) <- c(
  "timestamp",
  "gender",
  "age",
  "sex_active_age",
  "relationship_status",
  "open_relationship",
  "sexlife_satisfaction",
  "sexually_adventurous",
  "sex_active_current",
  "how_often_sex",
  "masturbate",
  "how_often_masturbate",
  "porn",
  "how_often_porn",
  "swinger",
  "swinger_clubs",
  "swinger_club_amount",
  "how_swinger",
  "do_friends_know_swinger",
  "swinger_affect",
  "how_swinger_affect",
  "sexparty",
  "how_often_sexparty",
  "how_sexparty",
  "do_friends_know_sexparty",
  "sexparty_affect",
  "how_sexparty_affect",
  "dom_sub",
  "dom_sub_enjoy",
  "dom_sub_freq",
  "bondage",
  "bondage_enjoy", 
  "bondage_freq", 
  "orgasm_control", 
  "orgasm_control_enjoy", 
  "orgasm_control_freq", 
  "virtual_sex",
  "virtual_sex_enjoy",
  "virtual_sex_freq", 
  "anal",
  "anal_enjoy", 
  "anal_freq",  
  "role_play", 
  "role_play_enjoy", 
  "role_play_freq", 
  "voyeur",
  "voyeur_enjoy", 
  "voyeur_freq",
  "public_sex", 
  "public_sex_enjoy",  
  "public_sex_freq", 
  "SandM", 
  "SandM_enjoy",  
  "SandM_freq", 
  "impact", 
  "impact_enjoy", 
  "impact_freq", 
  "dirty_talk", 
  "dirty_talk_enjoy", 
  "dirty_talk_freq", 
  "golden_showers", 
  "golden_shower_enjoy",  
  "golden_shower_freq",  
  "group_sex", 
  "group_sex_enjoy", 
  "group_sex_freq", 
  "cuckholding", 
  "cuckholding_enjoy", 
  "cuckholding_freq", 
  "age_play", 
  "age_play_enjoy",  
  "age_play_freq",  
  "foot_fetish", 
  "foot_fetish_enjoy", 
  "foot_fetish_freq", 
  "pegging", 
  "pegging_enjoy", 
  "pegging_freq", 
  "breath_control", 
  "breath_control_enjoy", 
  "breath_control_freq",
  "write_in_kinks",
  "where_interests_come_from",
  "final_thoughts"
  )

df <- tibble::rowid_to_column(df, "ID")

head(df)

```

```{r}
# renaming all the columns 
names(repo_df) <- c(
  "timestamp",
  "gender",
  "age",
  "nationality",
  "residence_country",
  "relationship_status",
  "open_relationship",
  "sex_active_years",
  "sexlife_satisfaction",
  "sexually_adventurous",
  "kink_curious",
  "masturbate",
  "how_often_masturbate",
  "porn",
  "how_often_porn",
  "swinger",
  "swinger_clubs",
  "swinger_club_amount",
  "how_swinger",
  "do_friends_know_swinger",
  "swinger_affect",
  "how_swinger_affect",
  "dom_sub",
  "dom_sub_enjoy",
  "dom_sub_freq",
  "bondage",
  "bondage_enjoy", 
  "bondage_freq", 
  "orgasm_control", 
  "orgasm_control_enjoy", 
  "orgasm_control_freq", 
  "virtual_sex",
  "virtual_sex_enjoy",
  "virtual_sex_freq", 
  "anal",
  "anal_enjoy", 
  "anal_freq",  
  "role_play", 
  "role_play_enjoy", 
  "role_play_freq", 
  "voyeur",
  "voyeur_enjoy", 
  "voyeur_freq",
  "public_sex", 
  "public_sex_enjoy",  
  "public_sex_freq", 
  "SandM", 
  "SandM_enjoy",  
  "SandM_freq", 
  "impact", 
  "impact_enjoy", 
  "impact_freq", 
  "dirty_talk", 
  "dirty_talk_enjoy", 
  "dirty_talk_freq", 
  "golden_showers", 
  "golden_shower_enjoy",  
  "golden_shower_freq",  
  "group_sex", 
  "group_sex_enjoy", 
  "group_sex_freq", 
  "cuckholding", 
  "cuckholding_enjoy", 
  "cuckholding_freq", 
  "age_play", 
  "age_play_enjoy",  
  "age_play_freq",  
  "foot_fetish", 
  "foot_fetish_enjoy", 
  "foot_fetish_freq", 
  "pegging", 
  "pegging_enjoy", 
  "pegging_freq", 
  "breath_control", 
  "breath_control_enjoy", 
  "breath_control_freq",
  "stag_vixen", 
  "stag_vixen_enjoy", 
  "stag_vixen_freq",
  "write_in_kinks",
  "taboo",
  "where_interests_come_from",
  "change_over_time",
  "why_change",
  "final_thoughts"
  )

repo_df <- tibble::rowid_to_column(repo_df, "ID")

head(repo_df)

```

###### Data cleaning ########## 
```{r}
# removing 'år' from the age columns 
df$age <- gsub("år","",as.character(df$age))

# removing from sex_active column
df$sex_active_age <- gsub("år","",as.character(df$sex_active_age))
df$sex_active_age <- gsub("(rape)","",as.character(df$sex_active_age))
# getting rid of () and wrote NA for the person who wrote 13/14 because I'm not using that info for this project
df[29,5] = "19"
df[60,5] = "NA"

# making man = 0, woman = 1, other = 2
df$gender <- ifelse(df$gender == 'Mand (Man)', '0', 
                    ifelse(df$gender == 'Kvinde (Woman)', '1' ,' 2'))
```

```{r}
# making yes = 1, no = 0

# making all yes = 1 and no = 0 
# Was inconsistent when creating the survey to have to fix that here 
df[df == 'Ja (Yes)'] <- '1'
df[df == 'Ja (yes)'] <- '1'
df[df == 'Ja, Yes'] <- '1'
df[df == 'Nej (No)'] <- '0'
df[df == 'Nej, No'] <- '0'
	
# getting rid of participant 180 because they only answered one question on the survey 
df <- df[-c(180),]
```

```{r}

# making man = 0, woman = 1, other = 2
repo_df$gender <- ifelse(repo_df$gender == 'Mand (Man)', '0', 
                    ifelse(repo_df$gender == 'Kvinde (Woman)', '1' ,' 2'))

repo_df[repo_df == 'Ja (Yes)'] <- '1'
repo_df[repo_df == 'Nej (No)'] <- '0'
```



# getting rid of the NAs in for the swinger affect column 
```{r}
club_affect <- subset(df, !is.na(how_swinger_affect))

repo_club_affect <- subset(repo_df, !is.na(how_swinger_affect))
```

Cuts it down to 66 and 62 participants 


```{r}
pacman::p_load(tidytext)
```


```{r}
# putting the desired column into it's own string 
club_affect <- club_affect$how_swinger_affect

repo_club_affect <- repo_club_affect$how_swinger_affect
```


```{r}
# splitting into lines 
club_affect_df <- data.frame(club_affect) %>% 
  mutate(text_full = str_split(club_affect, pattern = '\\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full))

repo_club_affect_df <- data.frame(repo_club_affect) %>% 
  mutate(text_full = str_split(repo_club_affect, pattern = '\\n')) %>% 
  unnest(text_full) %>% 
  mutate(text_full = str_trim(text_full))
```


```{r}
# splitting each line into words in the word column
club_affect_tokens <- club_affect_df %>% 
  unnest_tokens(word, text_full)

repo_club_affect_tokens <- repo_club_affect_df %>% 
  unnest_tokens(word, text_full)
```


```{r}
# counting the words 
club_affect_wc <- club_affect_tokens %>% 
  count(word) %>% 
  arrange(-n)
club_affect_wc
 
repo_club_affect_wc <- repo_club_affect_tokens %>% 
  count(word) %>% 
  arrange(-n)
repo_club_affect_wc

```

# Danish stop word list 
```{r}
pacman::p_load(stopwords)

length(stopwords::stopwords("da", source = "snowball"))
length(stopwords::stopwords("da", source = "nltk"))

# same length so likely fine to use either, also first 20 are the same when checked using the head() - can be used below 

#head(stopwords("da", source = "snowball"), n = 20) 
#head(stopwords("da", source = "nltk"), n = 20) 

dk_stopwords <- stopwords::stopwords("da", source = "snowball")

```

adding words to the stop list 
```{r}

new_stopwords <- c("f.eks", "fx", "osv", "3", "ik", "bl.a")

# appending the danish stop word list with a few specific to this data
dk_stopwords <- append(dk_stopwords,new_stopwords)

#new_stopwords <- c("bl.a")

# appending the danish stop word list with a few specific to this data
#dk_stopwords <- append(dk_stopwords,new_stopwords)
```


To do the next part, used code from this chat https://stackoverflow.com/questions/15253798/r-remove-stopwords-from-a-character-vector-using-in
```{r}
# creating a function that splits the words and then applies the stop words list and removes them 
with_stop <- unlist(lapply(club_affect_tokens$word , function(x) {paste(unlist(strsplit(x, " "))[!(unlist(strsplit(x, " ")) %in% dk_stopwords)], collapse=" ")}))

# needed to remove all the empty words there it was just "" marks 
with_stop <- with_stop[with_stop != ""]


repo_with_stop <- unlist(lapply(repo_club_affect_tokens$word , function(x) {paste(unlist(strsplit(x, " "))[!(unlist(strsplit(x, " ")) %in% dk_stopwords)], collapse=" ")}))


repo_with_stop <- repo_with_stop[repo_with_stop != ""]
```

```{r}
# showing how many unique words are in the word list 
length(unique(with_stop))

# making the character vector into a list 
with_stop_list <- as.list(with_stop)

# taking that list and putting it into one column of a data frame 
with_stop_df <- do.call(rbind.data.frame, with_stop_list)

# renaming that column 
colnames(with_stop_df) <- c('word')

# removing punctuation
club_affect_df$text_full <- gsub('[[:punct:] ]+',' ',club_affect_df$text_full)

top10 <- with_stop_df %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(11) # did top 11 because two words are iterations of the same 

top100 <- with_stop_df %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100) # did top 11 because two words are iterations of the same 

```

```{r}
# showing how many unique words are in the word list 
length(unique(repo_with_stop))

# making the character vector into a list 
repo_with_stop_list <- as.list(repo_with_stop)

# taking that list and putting it into one column of a data frame 
repo_with_stop_df <- do.call(rbind.data.frame, repo_with_stop_list)

# renaming that column 
colnames(repo_with_stop_df) <- c('word')

# removing punctuation
repo_club_affect_df$text_full <- gsub('[[:punct:] ]+',' ', repo_club_affect_df$text_full)

repo_top10 <- repo_with_stop_df %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(10) 

repo_top100 <- repo_with_stop_df %>% 
  count(word) %>% 
  arrange(-n) %>% 
  head(100) 

```

# word cloud 
```{r}

pacman::p_load(ggwordcloud)

# a very ugly not useful word cloud 
ggplot(data = repo_top100, aes(label = word)) +
  geom_text_wordcloud()# +
  #theme_minimal()

```



https://towardsdatascience.com/create-a-word-cloud-with-r-bde3e7422e8a
Like the look of both set.seed(7 & 12)
```{r}
par(mfrow=c(1,2)) # for 1 row, 2 cols

par(mar = c(1.5, 1.5, 1.5, 1.5))
set.seed(7) # for reproducibility 
wordcloud <- wordcloud(words = top100$word, freq = top100$n, min.freq = 1,           max.words=200, random.order=FALSE, rot.per=0.35,colors=brewer.pal(8, "Dark2"))

par(mar = c(1.5, 1.5, 1.5, 1.5))
set.seed(7) # for reproducibility 
wordcloud(words = repo_top100$word, freq = repo_top100$n, min.freq = 1, max.words=200, random.order=FALSE, rot.per=0.35,colors=brewer.pal(8, "Dark2"))


```


#SENTIDA 
work on strings so should look at each persons response and not just the individual words sentiment 

```{r}
if(!require("devtools")) install.packages("devtools")

#devtools::install_github("Guscode/Sentida")

library(Sentida)
```

getting sentiment scores for each response 
```{r}
# applying sentida and creating a new column for the results of total sentiment
club_affect_df$sentiment <- lapply(club_affect_df$text_full, sentida, output = "total")

# same as above but creating another column for the phrases mean sentiment 
club_affect_df$avg_sentiment <- lapply(club_affect_df$text_full, sentida, output = "mean")

# random cross checking 
sentida("Jeg er blevet mere eventyrlysten.", output = "total")

sentida("Udvidet horisonter Ting man før fandt ekstreme og unormale er med tiden blevet mere normaliseret", output = "total") 

sentida("Udvidet horisonter Ting man før fandt ekstreme og unormale er med tiden blevet mere normaliseret", output = "mean") 


sentida("Blev introduceret for bdsm og jeg fandt det jeg manglede", output = "mean")
sentida("Blev", output = "mean") # neutral
sentida("introduceret", output = "mean") # slight pos
sentida("for", output = "mean") # neutral
sentida("bdsm", output = "mean") # neutral
sentida("og", output = "mean") # neutral
sentida("jeg", output = "mean") # neutral
sentida("fandt", output = "mean") # very negative 
sentida("det", output = "mean") # neutral 
sentida("manglede", output = "mean") # neutral 

```


```{r}

# applying sentida and creating a new column for the results of total sentiment
repo_club_affect_df$sentiment <- lapply(repo_club_affect_df$text_full, sentida, output = "total")

# same as above but creating another column for the phrases mean sentiment 
repo_club_affect_df$avg_sentiment <- lapply(repo_club_affect_df$text_full, sentida, output = "mean")

sentida("At jeg er til bdsm hvilket jeg ikke vidste før swingerlivet", output = "total") 

sentida("At jeg er til bdsm hvilket jeg ikke vidste før swingerlivet", output = "mean") 


sentida("At", output = "mean") # neutral
sentida("jeg", output = "mean") # neutral 
sentida("er", output = "mean") # neutral
sentida("til", output = "mean") # neutral
sentida("bdsm", output = "mean") # neutral
sentida("hvilket", output = "mean") # neutral
sentida("ikke", output = "mean") # neutral 
sentida("vidste", output = "mean") # neutral 
sentida("før", output = "mean") # pos
sentida("swingerlivet", output = "mean") # neutral 

```
Checked a negatively rated phrase but each word is neutral or positive. 

making sentiment columns numeric
```{r}
club_affect_df <- club_affect_df %>% 
  mutate_at(c('sentiment', 'avg_sentiment'), as.numeric)

repo_club_affect_df <- repo_club_affect_df %>% 
  mutate_at(c('sentiment', 'avg_sentiment'), as.numeric)

```


# plotting 
```{r}
# histogram 
hist(club_affect_df$avg_sentiment)
hist(club_affect_df$sentiment)

# ggplot 

avg_hist <- ggplot(club_affect_df, aes(x = avg_sentiment))+
  geom_histogram(aes(y = ..density..), color = "darkblue", fill = "lightblue") +
  labs(x = "Avg sentiment", y = "density")


hist <- ggplot(club_affect_df, aes(x = sentiment))+
  geom_histogram(aes(y = ..density..), color = "darkblue", fill = "lightblue")  +
  labs(x = "Total sentiment", y = "density")

# putting the two graphs side by side in the same graphic 
hist_combo <- ggarrange(hist, avg_hist, ncol = 2, nrow = 1)

#give them a shared title 
hist_combo <- annotate_figure(hist_combo, top = text_grob("Original study", 
               color = "black", face = "bold", size = 14))
hist_combo
```

```{r}
# histogram 
hist(repo_club_affect_df$avg_sentiment)
hist(repo_club_affect_df$sentiment)

# ggplot 

repo_avg_hist <- ggplot(repo_club_affect_df, aes(x = avg_sentiment))+
  geom_histogram(aes(y = ..density..), color = "darkblue", fill = "lightblue") +
  labs(title = "Average sentiment of each responses", x = "Avg sentiment", y = "density")

repo_hist <- ggplot(repo_club_affect_df, aes(x = sentiment))+
  geom_histogram(aes(y = ..density..), color = "darkblue", fill = "lightblue") +
  labs(title = "Total sentiment of each response", x = "Total sentiment", y = "density")

  
# putting the two graphs side by side in the same graphic 
repo_hist_combo <- ggarrange(repo_hist, repo_avg_hist, ncol = 2, nrow = 1)

#give them a shared title 
repo_hist_combo <- annotate_figure(repo_hist_combo, top = text_grob("Reproduced study", 
               color = "black", face = "bold", size = 14))
repo_hist_combo
```


```{r}
ggarrange(hist_combo, repo_hist_combo, ncol = 1, nrow = 2)
```

Could also do a bar graph of positive, negative, and neutral bars...

```{r}
# assigning positive or negative valance based on Sentida's sentiment 
club_affect_df$valence <- ifelse(club_affect_df$sentiment > 0, 'positive', 'negative')

# get the sentiment count  
club_affect_df %>%
  count(valence) 

plot <- ggplot(club_affect_df, aes(x=valence, fill = valence))+
  labs(title = "Original study", x = "Senitment", y = "Count") +
  geom_bar(position = "dodge") +
  theme(plot.title = element_text(size=11)) +
  theme(axis.title = element_text(size = 9)) +
  scale_fill_manual(values=c("#08519C", "#0c77e5")) +
  rremove("legend")
plot
```

```{r}

# assigning positive or negative valance based on Sentida's sentiment 
repo_club_affect_df$valence <- ifelse(repo_club_affect_df$sentiment > 0, 'positive', 'negative')

# get the sentiment count 
repo_club_affect_df %>%
  count(valence) 

repo_plot <- ggplot(repo_club_affect_df, aes(x=valence, fill = valence))+
  labs(title = "Reproduced study", x = "Senitment", y = "Count") +
  geom_bar(position = "dodge") +
  theme(plot.title = element_text(size=11)) +
  theme(axis.title = element_text(size = 9)) +
  scale_fill_manual(values=c("#08519C", "#0c77e5")) +
  rremove("legend")
repo_plot
```

```{r}
ggarrange(plot, repo_plot, ncol = 2, nrow = 1,
          labels = c("(a)", "(b)"))
```


summary stats 
```{r}
# for avg sentiment
summary <- club_affect_df %>% 
  summarize(
    mean_score = mean(avg_sentiment),
    median_score = median(avg_sentiment),
    sd_score = sd(sentiment)
  )
summary

# for total sentiment 
summary2 <- club_affect_df %>% 
  summarize(
    mean_score = mean(sentiment),
    median_score = median(sentiment),
    sd_score = sd(sentiment)
  )
summary2
```


```{r}
# for avg sentiment
repo_summary <- repo_club_affect_df %>% 
  summarize(
    mean_score = mean(avg_sentiment),
    median_score = median(avg_sentiment),
    sd_score = sd(avg_sentiment),
  )
repo_summary

# for total sentiment 
repo_summary2 <- repo_club_affect_df %>% 
  summarize(
    mean_score = mean(sentiment),
    median_score = median(sentiment),
    sd_score = sd(sentiment)
  )
repo_summary2

```

# T-test 
Running a t-test between the two survey's to see if there's a difference in avg sentiment and total sentiment

```{r}
avg_ttest <- t.test(repo_club_affect_df$avg_sentiment, club_affect_df$avg_sentiment)
avg_ttest

ttest <- t.test(repo_club_affect_df$sentiment, club_affect_df$sentiment)
ttest
```
No difference in average sentiment but there is between the total sentiment of the two surveys, mean higher with the original survey... Unsure why 


# Package Info 

```{r}
sessionInfo()
```

# Citing packages 

```{r}
library(purrr)

c("stopwords", "tidytext", "ggwordcloud", "SnowballC", "wordcloud", "RColorBrewer", "tm", "rstatix", "dplyr") %>%
  map(citation) %>%
  print(style = "text")
```
