---
title: "HW6 - Practicing functions with Gapminder"
author: "Anja Meerwald"
date: "10/30/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(gapminder)

# taking the gapminder data and turning it into a dataframe 
df <- as.data.frame(gapminder)
```

1. Define a defensive function that calculates the Gross Domestic Product of a nation from the data available in the gapminder dataset. You can use the population and GDPpercapita columns for it. Using that function, calculate the GDP of Denmark in the following years: 1967, 1977, 1987, 1997, 2007, and 2017.

```{r}

# creating the function, used from https://swcarpentry.github.io/r-novice-gapminder/10-functions/index.html

calcGDP <- function(dat, year=NULL, country=NULL) { # defining the name of the function and which variables are included. They will be null if not specified 
  if(!is.null(year)) {   # if it's not null, then...
    dat <- dat[dat$year %in% year, ]   # creates a temporary variable dat which takes the subsetted data by year if it's specified 
  }
  if (!is.null(country)) {
    dat <- dat[dat$country %in% country,]  # same as above, subsetting by country if provided 
  }
  gdp <- dat$pop * dat$gdpPercap  # calculating the gdp with the population and gdpPercap variables 

  new <- cbind(dat, gdp=gdp) # pputs that subsetted data from above with a new gdp column and treturns the result 
  return(new)
}

# calculating Denmark's GDP in the specified years except for 2017 because it's not included in the dataset 
calcGDP(gapminder, country = "Denmark", year = c(1967, 1977, 1987, 1997, 2007, 2017))
```

2. Write a script that loops over each country in the gapminder dataset, tests whether the country starts with a ‘B’ , and prints out whether the life expectancy is smaller than 50, between 50 and 70, or greater than 70. (Hint: remember the grepl function, and review the Control Flow tutorial)

```{r}

lowerThreshold <- 50
upperThreshold <- 70


B_countries <- grep("^B", unique(df$country), value = TRUE) # using grep to find countries that start with 'B' and assigning them to the new variable, B_countries

for (iCountry in B_countries) {    # looping through the countries within the B_countries variable 
    tmp <- mean(df[df$country == iCountry, "lifeExp"])   # getting the mean life expectancy 
# using the lower and upper thresholds to determine the printed output 
    if (tmp < lowerThreshold) {   
        cat("Average Life Expectancy in", iCountry, "is less than", lowerThreshold, "\n") # if the life expectancy is less than 50, print it's less than
    } else if(tmp > lowerThreshold && tmp < upperThreshold) {   # if the life expectancy is between 50-70, print it is between
        cat("Average Life Expectancy in", iCountry, "is between", lowerThreshold, "and", upperThreshold, "\n")
    } else {
        cat("Average Life Expectancy in", iCountry, "is greater than", upperThreshold, "\n") # and if it's greater than 70, print that
    } # end if
    rm(tmp)
} # end for loop

```

3. Challenge/Optional: Write a script that loops over each country in the gapminder dataset, tests whether the country starts with a ‘M’ and graphs life expectancy against time (using plot() function) as a line graph if the mean life expectancy is under 50 years.

```{r}

thresholdValue <- 50 # setting the threshold to 50 years 
candidateCountries <- grep("^M", unique(gapminder$country), value = TRUE) # using grep to find countries that start with 'M' and assigning them to the new variable, M_countries

for (iCountry in candidateCountries) {   # looping through the countries within the M_countries variable 
    tmp <- mean(df[df$country == iCountry, "lifeExp"]) # calculating mean life expectancy 

    if (tmp < thresholdValue) { # if the mean life expectancy is less than the threshold (50), print that and the plot it 
        cat("Average Life Expectancy in", iCountry, "is less than", thresholdValue, "plotting life expectancy graph... \n")

        with(subset(gapminder, country == iCountry),  # 
                plot(year, lifeExp,
                     type = "o",
                     main = paste("Life Expectancy in", iCountry, "over time"),
                     ylab = "Life Expectancy",
                     xlab = "Year"
                     ) # end plot
             ) # end with
    } # end if
    rm(tmp)
}

```


